\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[charter]{mathdesign}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

% Don't print section numbers
\titleformat{\section}%
  [hang]% <shape>
  {\normalfont\scshape\Large}% <format>
  {}% <label>
  {0pt}% <sep>
  {}% <before code>

% Restyle bulleted lists
\renewcommand{\labelitemi}{}
\setlist[itemize,1]{leftmargin=0ex}

% Consistency with provided Pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\begin{center}
  {%
    \huge\bf%
    Brenton Kenkel%
  }%

  \vspace{0.5em}

  {%
    \Large%
    Curriculum Vitae%
  }%
\end{center}

\section{Contact Information}\label{contact-information}

\begin{description}
\tightlist
\item[Email]
\href{mailto:brenton.kenkel@vanderbilt.edu}{\texttt{brenton.kenkel@vanderbilt.edu}}
\item[Web]
\url{http://bkenkel.com}
\item[Phone]
615-875-8345
\item[Mailing]
324 Commons\\
Vanderbilt University\\
PMB 0505\\
Nashville, TN 37203
\end{description}

\section{Employment}\label{employment}

\begin{itemize}
\item
  \textbf{Vanderbilt University}, Nashville, TN\\
  Assistant Professor, Department of Political Science, 2014-present
\item
  \textbf{Princeton University}, Princeton, NJ\\
  Senior Research Assistant (predoctoral fellow), Department of
  Politics, 2013-2014.
\end{itemize}

\section{Education}\label{education}

\begin{itemize}
\item
  \textbf{University of Rochester}, Rochester, NY\\
  Ph.D., Political Science, 2014.\\
  M.A., Political Science, 2011.
\item
  \textbf{University of Kentucky}, Lexington, KY\\
  B.A., Political Science, 2008.\\
  B.A., Philosophy, 2008.
\end{itemize}

\section{Publications}\label{publications}

\begin{itemize}
\item
  Robert J. Carroll and Brenton Kenkel,
  \href{http://bkenkel.com/data/doe.pdf}{``Prediction, Proxies, and
  Power,''} conditionally accepted at \emph{American Journal of
  Political Science}.
\item
  Kevin A. Clarke, Brenton Kenkel, and Miguel R. Rueda,
  \href{http://www.rochester.edu/college/psc/clarke/MissProp.pdf}{``Omitted
  Variables, Countervailing Effects, and the Possibility of
  Overadjustment,''} forthcoming at \emph{Political Science Research and
  Methods}.
\item
  Mark Fey, Jinhee Jo, and Brenton Kenkel,
  \href{http://dx.doi.org/10.1177/0022002713503285}{``Information and
  International Institutions Revisited,''} \emph{Journal of Conflict
  Resolution} 59, no. 1 (2015).
\item
  Brenton Kenkel and Curtis S. Signorino,
  \href{http://www.jstatsoft.org/v56/i08}{``Estimating Extensive Form
  Games in R,''} \emph{Journal of Statistical Software} 56, no. 8
  (2014).
\end{itemize}

\section{Working Papers}\label{working-papers}

\begin{itemize}
\item
  \href{http://bkenkel.com/data/divconq.pdf}{``Dividing the Conquered''}
\item
  \href{http://bkenkel.com/data/talk.pdf}{``Information and
  Communication in Public Goods Problems''}
\item
  \href{http://bkenkel.com/data/idlogit.pdf}{``A General Solution to
  Nonignorable Missing Outcomes in Binary Choice Data''}
\item
  \href{http://bkenkel.com/data/valence.pdf}{``Campaign Spending and
  Hidden Policy Intentions''}
\item
  ``Is an Ultimatum the Last Word on Crisis Bargaining?'' (with Mark
  Fey)
\item
  ``A Quantitative Bargaining Theory of War'' (with Kristopher W.
  Ramsay)
\item
  \href{http://bkenkel.com/data/basics.pdf}{``Boostrapped Basis
  Regression with Variable Selection: A New Method for Flexible
  Functional Form Estimation''} (with Curtis Signorino)
\item
  \href{http://polmeth.wustl.edu/mediaDetail.php?docId=1278}{``Data
  Mining for Theorists''} (with Curtis Signorino)
\item
  \href{http://polmeth.wustl.edu/mediaDetail.php?docId=1359}{``An
  Alternative Solution to the Heckman Selection Problem: Selection Bias
  as Functional Form Misspecification''} (with Curtis Signorino)
\end{itemize}

\section{Awards and Grants}\label{awards-and-grants}

\begin{itemize}
\item
  2012. Wallis Institute of Political Economy PEPR Grant (with Curtis
  Signorino).
\item
  2011. Society for Political Methodology Poster Award.
\item
  2010. Wallis Institute of Political Economy PEPR Grant (with Curtis
  Signorino).
\item
  2010. Prize for Excellence in Teaching by a Graduate Student,
  University of Rochester Department of Political Science.
\end{itemize}

\section{Courses Taught}\label{courses-taught}

\begin{itemize}
\tightlist
\item
  \textbf{Vanderbilt University}

  \begin{itemize}
  \tightlist
  \item
    \href{http://bkenkel.com/psci2220}{PSCI 2220: Crisis Diplomacy}
    (undergraduate)
  \item
    \href{http://bkenkel.com/psci221}{PSCI 2221: Causes of War}
    (undergraduate)
  \item
    \href{http://bkenkel.com/psci8357}{PSCI 8357: Statistics for
    Political Research II} (graduate)
  \item
    PSCI 8360: Models of International Conflict (graduate)
  \item
    Math boot camp (incoming Ph.D.~students)
  \end{itemize}
\item
  \textbf{University of Rochester}

  \begin{itemize}
  \tightlist
  \item
    Math Pre-fresher (incoming Ph.D.~students)
  \item
    \href{https://github.com/brentonk/rcourse}{Short Course on R}
    (first-year Ph.D.~students)
  \end{itemize}
\end{itemize}

\section{Invited Presentations}\label{invited-presentations}

\begin{itemize}
\item
  2017. Political Economy Workshop, University of Chicago Harris School.
\item
  2016. Conference on Formal Models of International Relations,
  University of Southern California.
\item
  2015. Conference on Empirical Implications of Bargaining Theory,
  Princeton University.
\item
  2014. Workshop on Empirical Implications of the Bargaining Model of
  War, Peace Science Society annual meeting.
\item
  2013. Conference on Theoretical and Quantitative International
  Relations Research, Princeton University.
\item
  2013. Mathematical Modeling of Political Behavior Conference,
  University at Buffalo.
\item
  2012. New Faces in Political Methodology, Penn State University.
\end{itemize}

\section{Conference Presentations}\label{conference-presentations}

\begin{itemize}
\tightlist
\item
  American Political Science Association: 2011, 2013, 2014, 2016
\item
  Midwest Political Science Association: 2012--2015
\item
  Southern Political Science Association: 2013, 2016
\item
  Peace Science Society (International): 2011, 2014--2015
\item
  Society for Political Methodology: 2010--2012, 2015
\item
  International Studies Association: 2016
\end{itemize}

\section{Software}\label{software}

\begin{itemize}
\item
  \texttt{games}: statistical estimation of game-theoretic models (with
  Curtis Signorino).
  \url{http://cran.r-project.org/web/packages/games/index.html}
\item
  \texttt{polywog}: bootstrapped basis regression with oracle model
  selection (with Curtis Signorino).
  \url{http://cran.r-project.org/web/packages/polywog/index.html}
\end{itemize}

\section{Professional Service}\label{professional-service}

\begin{itemize}
\item
  Reviewer for: \emph{Conflict Management and Peace Science},
  \emph{International Interactions}, \emph{International Organization},
  \emph{Journal of Peace Research}, \emph{Journal of Politics},
  \emph{Public Choice}, \emph{Social Choice and Welfare}, \emph{World
  Politics}
\item
  Professional associations:

  \begin{itemize}
  \tightlist
  \item
    American Political Science Association (2008--present)
  \item
    Midwest Political Science Association (2012--present)
  \item
    Peace Science Society (2014--present)
  \end{itemize}
\end{itemize}

\section{References}\label{references}

Available on request.


\end{document}
